Measuring causal influence with\\ back-to-back regression: the linear case - supplementary material

### 2019-05-23 paper/introduction.tex
typo

The second challenge to measuring causal influence is that observations can be large and complex. The relationship between causes and effects is thus often considered in a backward manner, by training models to maximally predict causes from multidimensional observations. For example, brain activity is often recorded with hundreds or thousands of sensors simultaneously. It is thus common to use `decoding' techniques, by, for example, fitting a support vector machine across multiple sensors to predict the category of a stimulus \citep{cichy2014resolving, king2016brain, kriegeskorte2008representational, norman2006beyond}.

>>>>

The second challenge to measuring causal influence is that observations can be large and complex. The relationship between causes and effects is thus often considered in a backward manner, by training models to maximally predict causes from multidimensional observations. For example, brain activity is often recorded with hundreds or thousands of sensors simultaneously. It is thus common to use `decoding' techniques, by, for example, fitting a support vector machine across multiple sensors to predict the category of a stimulus \citep{cichy2014resolving,  kriegeskorte2008representational, norman2006beyond}.
